%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\usepackage[utf8]{inputenc}
\usepackage[T5]{fontenc}
\usepackage[vietnamese]{babel}
%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Nguyễn Nam Quân} \\[7.5pt]
\href{https://github.com/NamQuanProject}{\raisebox{-0.05\height}\faGithub\ NamQuanProject} \ $|$ \ 
\href{https://www.linkedin.com/in/nnquan23/}{\raisebox{-0.05\height}\faLinkedin\ Nam Quan Nguyen} \ $|$ \ 
\href{nnquan23@apcs.fitus.edu.vn}
{\raisebox{-0.05\height}\faEnvelope \ nnquan23@apcs.fitus.edu.vn} \ $|$ \ 
\href{tel:+000000000000}{\raisebox{-0.05\height}\faMobile \ +84 09.15.794.463} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Motivated AI practitioner with experience in machine learning research, model development, and practical system building. I work with modern deep learning techniques, including model editing, continual learning, and multimodal systems. I have contributed to academic projects and real-world applications involving data analysis, visualization, and AI-assisted tools. I aim to strengthen my expertise through research, engineering, and collaboration on impactful AI projects.

%Experience
\section{Work Experience}
\begin{joblong}{SAB}{Sep 2021 -- Sep 2023}
\item \textbf{Academic Assosiates}: Supported academic operations and coordinated learning activities for students.
\item \textbf{Head of Academy}: Led academic planning and contributed to improving internal workflows.
\end{joblong}
\begin{joblong}{SELAB}{Jan 2022 -- Present}
\item \textbf{Research Assistance} Assisted in machine learning research and experimentation. 
\item \textbf{Lab Researcher:} Contributed to projects involving multimodal processing for downstream task like segmentation, classification
\end{joblong}
\begin{joblong}{AISIA-LAB}{Sep 2024 -- Present}
\item \textbf{Research Assistant} Supporting on medical processing on bacterial segmentation and data processing. 
\end{joblong}


\section{Projects}

\noindent
\makebox[\linewidth][s]{%
\textbf{OuterHomes}%
\hfill
\href{https://github.com/AdamHermes/NASA-Space-Apps-Challenge-2025}{Backend} \,|\,
\href{https://github.com/lammhuyy/NASA-Space-Apps-Challenge-2025-frontend}{Frontend}%
}

A web application for seamless machine learning model training and Kepler light-curve visualization:
\begin{itemize}[nosep,leftmargin=1em]
    \item Endpoints for processing, inference, model training, and visualization.
    \item Custom dataset utilities, ensemble models, and a PyTorch CNN+Attention classifier.
\end{itemize}

\vspace{6pt}

\noindent
\makebox[\linewidth][s]{%
\textbf{FoodMark}%
\hfill
\href{https://github.com/Noridom1/FoodMark-backend}{Backend} \,|\,
\href{https://github.com/Noridom1/CS426_MobileProject}{Frontend}%
}
FoodMark is an application that allows users to share food-related videos. The app automatically extracts and organizes useful information, mapping restaurants or breaking down recipes into clear steps. This turns passive viewing into active exploration, allowing users to revisit and act on their discoveries.

\vspace{6pt}

\noindent
\makebox[\linewidth][s]{%
\textbf{AIRS — AI Recruitment Assistant}%
\hfill
\href{https://github.com/NamQuanProject/Recruiment_Assistant}{Full Project}%
}
The AI-Powered Recruitment System is an intelligent recruitment assistant designed to automate the analysis and evaluation of resumes (CVs) based on job descriptions (JDs) provided by employers. By leveraging cutting-edge AI models, the system can:
\begin{itemize}[nosep,leftmargin=1em]
    \item Provides fairness-oriented scoring and explainable recommendations.
    \item Validates details in resumes and reduces bias during the evaluation process.
\end{itemize}

\vspace{6pt}

\noindent
\makebox[\linewidth][s]{%
\textbf{AI-Driven Research Assistance Tools With Fact Connections}%
\hfill
\text{ }%
}
An AI-driven research tool that analyzes, verifies, and connects facts across multiple sources, streamlining literature reviews, enhancing fact-checking meaningful relationships between concepts. By automating information synthesis, it helps researchers efficiently discover and improve knowledge discovery.



%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Education}



\begin{tabularx}{\linewidth}{@{}l X@{}}	
2020 - 2023 & High School \textbf{Luong Van Chanh  for the gifted} \hfill \normalsize (GPA: 3.84/4.0) \\


2025 - present & Pursuing Bachelor's Degree \textbf{VNUHCM- University of Science} \hfill \normalsize (GPA: 3.68/4.0) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}

Programming & Python, JavaScript, HTML, Go, Kotlin, C++, SQL \\

Machine Learning & Deep Learning, Model Editing, Continual Learning, Computer Vision, NLP, Multimodal Learning, Diffusion, Transfer Learning \\

Frameworks & PyTorch, TensorFlow/Keras, HuggingFace Transformers, Ultralytics, OpenCV, scikit-learn, ReactJS \\

AI Engineering & Training pipelines, data preprocessing, experiment tracking, evaluation metrics, FastAPI deployment, optimization, debugging \\

App Development & Jetpack Compose, Clean Architecture, Kotlin Coroutines, Supabase Auth, Firebase, SQL databases \\

Tools & Git, Docker, Linux, LaTeX, Overleaf, Postman, Android Studio, Jupyter \\

Clout Technologies & AWS, Google Cloud Platform, Firebase,
Microsoft Azure, Vercel, Supabase
\\

Language & Vietnamese (MT), English (IELTS 7.0), Chinese (HSK1) \\

\end{tabularx}
\end{document}
